PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2021-09-30 main.tex
Material for figure 1
Add more figures
Add reference to wallace 2017

@@

@@

@@

>>>>

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/alpha_beta.png}
    \caption{Caption goes here.\label{fig:alpha_beta}}
\end{center}
\end{figure*}

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/alpha_beta_evo.png}
    \caption{Caption goes here.\label{fig:alpha_beta_evo}}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/fulldisk_e_m.png}
    \caption{Caption goes here.\label{fig:fulldisk_e_m}}
\end{center}
\end{figure*}

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/alpha_pl_frac.png}
    \caption{Caption goes here.\label{fig:alpha_pl_frac}}
\end{center}
\end{figure}

@@

% is there a clever, succinct way to show the evolution of sigma/Sigma in each period bin? to demonstrate that the accretion boundary is static

@@

How to reconcile our concerns with the results of \citet{wallace17}?
